---
title: 'lab: multiple linear regression'
author: "Sage Davis"
date: "11/9/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(palmerpenguins)
library(GGally)
library(broom)
library(kableExtra)
library(modelsummary)
library(stargazer)

```

explore penguins

```{r}
ggpairs(penguins)
```


Lets simplefy the variable that wee include:
- species
bill-LENGTH_mm,through body_mass_g

```{r}
penguins %>% 
  select(species, bill_length_mm:body_mass_g) %>% 
  ggpairs(aes(color = species))

```

we RE GOING TO PERFOR MULTIPLE LINEAR REGRESSION

trying to understand   bit better  relationships between multiple predictor variables and an outcome which is penguin body mass

- species
- flipper length
- sex
- bill depth

bad idea ( there are importabt vars missing)

```{r}
model_1 <- lm(body_mass_g ~ flipper_length_mm + bill_depth_mm, data = penguins)


# Call model
model_1

# above does the same thing
#summary(model_1)
```

If all other things are held contsant, for each 1 mm of flipper length there will be a 51.5g (use inline code) increase in body mass.

Pr 9% > 5%, so retain the null hypothesis.

R^2: 7596% of the variance in penguin body is explained by the model (or penguin bill and flipper length)

Actually we think  this should contain sex as well.

```{r}
model_2 <- lm(body_mass_g ~ flipper_length_mm + species + sex, data = penguins)

model_2
```
Lecture yesterday
 reference is Adelle penguin
 reference is sexfemale
 
INtrepret:
if all things remain constant, for every 1 mm fof flipper_length will increase body mass by 20.02

if all thing remain constant, on average we expect the penguin is Gentoo (male) then the body mass will be 836g (530g) larger than an an Adelle (female)


## visualize this model - on average male is 530g larger so is Adelle is 836g larger - does it look right

```{r}
ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g)) +
  geom_point(aes(color = species)) +
  facet_wrap(~sex)

```


a aciuple ways to get an report are:

broon::tidy() to get model coeff into in a tidy day a model

```{r}
penguin_model_coef <- tidy(model_2)

penguin_model_coef
```

Gentu: `r penguin_model_coef$estimate[4]`

Look at model diag

use plot()

```{r}
plot(model_2)

summary(model_2)
```

report moel in a table

```{r}
modelsummary(model_2)
```
use stargazer

```{r, results = "asis"}

stargazer(model_2, type = "html")

stargazer(model_1, model_2, type = "html")
```

